% !TEX root = ../../thesis.tex
%
\hfill
\begin{center}
\textbf{{\Large \thesisTitle}}\\
% \vspace{0.5cm}
% \textbf{{\large \thesisName}}\\
\end{center}

\begin{abstract}
A brain tumor is a growth of cells in the brain or near it. Brain tumors can happen in the brain tissue. Brain tumors also can happen near the brain tissue. Nearby locations include nerves, the pituitary gland, the pineal gland, and the membranes that cover the surface of the brain.

Your skull, which encloses your brain, is very rigid. Any growth inside such a restricted space can cause problems. Brain tumors can be of two types i.e. cancerous (malignant) or non-cancerous (benign). 

Brain cancer is a life-threatening disease, and it affects all the diagnosed people severely. Precise brain tumor classification helps to diagnose brain cancer early, which increases the survival rate of brain cancer patients, but it is quite hard to detect early. It is difficult to evaluate the magnetic resonance imaging images manually. Therefore, there is a need for optimized and fast digital methods for tumor diagnosis with better accuracy. 

In this work, we are using a deep learning model based on convolutional neural networks to identify and classify brain cancer and its type from MRI images of patients using a publicly available dataset in Kaggle \cite{br35h}. 

For brain stroke, is a brain attack and it is a sudden interruption of continuous blood flow to the brain and a medical emergency. A stroke occurs when a blood vessel in the brain becomes blocked or narrowed, or when a blood vessel bursts and spills blood into the brain.

Stroke is a major contributor to death and disability worldwide. Prior to modern therapy, post-stroke mortality was approximately 10\% in the acute period, with nearly one-half of the patients developing moderate-to-severe disability. 

The most fundamental aspect of acute stroke management is “time is brain”. In acute ischemic stroke, the primary therapeutic goal of reperfusion therapy, including intravenous recombinant tissue plasminogen activator (IV TPA) and/or endovascular thrombectomy, is the rapid restoration of cerebral blood flow to the salvageable ischemic brain tissue at risk for cerebral infarction. 

Several landmark endovascular thrombectomy trials were found to be of benefit in selecting patients with acute stroke caused by occlusion of the proximal anterior circulation, which has led to a paradigm shift in the management of acute ischemic strokes. 

In this modern era of acute stroke care, more patients will survive with varying degrees of disability post-stroke. A comprehensive stroke rehabilitation program is critical to optimize post-stroke outcomes. Understanding the natural history of stroke recovery, and adapting a multidisciplinary approach, will lead to improved chances for successful rehabilitation.

Here we are using a CNN model for deep learning multi-image classification which classifies input images into tumor, no tumor, stroke, or no stroke.


\end{abstract}

\vfill
    {\small Supervisors: \thesisFirstSupervisor\ and \thesisSecondSupervisor}
