%!TEX root = ../../thesis.tex
\chapter{Literature Review}

To begin research, it is necessary to write a review. It's critical to have access to old publications on topics like space and application, both of which are associated with the kind of work we do. It's not difficult to determine the real demand, the drawbacks of previous labor, and the weight of work after conducting a thorough examination of the past. Using reference papers helps students comprehend the work, calculations, models, and previous research used, as well as pointing them in the right direction for future study. Deep learning and machine learning frameworks are reviewed in this section.

\section{Fundamental Concepts}
\subsection{Data}

Fusion is nothing but a combination of data from various sources; these sources can be homogeneous or heterogeneous. It provides the result in some sense better than the individual input. Input from various sources gives a more accurate result than depending on only a single input in the case of various automatic applications \cite{dattaad:10.1504}.


\subsection{Sensor Fusion}

Sensor fusion technology is widely used in automatic applications. The collection of separate data from various sensors is done in sensor fusion. This technology leads to accurate and reliable results than depending on the not-that-accurate result from a single sensor. This technology uses microcontrollers for this work.

Sensor technology is evolving day by day and similarly trying to act like an actual human being. Because of its precision and ability to perform well this technology is used in various applications such as climate monitoring, healthcare, automotive systems, smart mobile devices, industrial control, and oil exploration.

\subsection{Machine Learning}

Throughout the 1980s and 1990s, the use of information-driven Artificial Intelligence (AI) tactics in many building fields, such as voice and picture analysis, grew in popularity. As indexes of structured knowledge grow, using robots to extract relevant instances from the data may be a game-changer.

An inquiry requires a large quantity of information, and it's difficult to examine all the potential linkages and connections with distinct connections of information sources that might produce many outcomes and can be investigated in detail to get desired results.


Artificial intelligence (AI) and Machine learning (ML) are ideal to unlock the full potential of massive data. Artificial intelligence (AI) is fully integrated within machine learning to help systems learn and grow without needing to be directly programmed.

Machine learning occurs when a computer is given a large amount of data, and the computer uses that data to figure things out for itself. Artificial intelligence may benefit from it because of the improved method it gives for its construction. Automated decision-making is a key feature of machine learning, which is why it is so commonly utilized \cite{masood900}.

\subsection{Supervised Learning}

\begin{enumerate}[a)]
    \item Data must be prepared for the train machine. This data is known as training data. The technique in which the training data is learned from supervised algorithms and gives some results depending on them was nominated as a supervised learning algorithm.
    \item Supervised learning is of two types; these types are regression and classification.
    \item Sometimes there is a risk of receiving some unrelated input from training data.
    \item Once the machine learns from supervised learning it keeps the record and whenever some data output is needed it gives that output using such previous work.
    \item The Kind of data sets needed to be used in machine learning must be decided first to consider how best-supervised learning works
\end{enumerate}

\subsection{Unsupervised Learning}

\begin{enumerate}[a)]
    \item There is no requirement to supervise the model in unsupervised machine learning.
    \item If there are unknown patterns present in data then these unknown patterns are recognized by unsupervised machine learning.
    \item There are two types of unsupervised learning: clustering and second is association.
    \item In this unsupervised learning technique four types of clustering methods are used. These clustering methods are exclusive, agglomerative, overlapping, and probabilistic.
    \item There are large databases that are involved these databases have data objects in them. These data objects need association between themselves. To do this association rules are required.
    \item Whenever data is sorted in process it is not possible to get precise information is the drawback of this unsupervised learning.
\end{enumerate}

\subsection{Reinforcement Learning}

\begin{enumerate}[a)]
    \item Sequence is very important in reinforcement learning. Simply output is dependent on the current input and for the input of the next stage; the output of the previous stage is required.
    \item Dependency is there in reinforcement learning so there is a need to assign labels to each dependent decision.
    \item This technique broadens its area of training by taking help from the environment instead of just depending on the data set provided so that it can increase the chances of better output.
\end{enumerate}

\subsection{ Statistics and Probability in Machine Learning}

 Machine learning is mainly involved in building intelligent applications. To make intelligent application statistics and probability algorithms are used in terms of providing better vision by learning from data.

To predict upcoming events probability is used and to analyze the events in the past statistics is used.

\subsection{Decision Making}

 Decision-making is very important as it provides one conclusive stage to the system. A decision tree has branches and leaves. Branches denote observations and leaves represent conclusions, so the overall decision tree is used as a predictive model. Data mining, statistics, and machine learning need accurate decision making so it uses this approach of predictive modeling. Every leaf of the tree has a class label, and branches connect the leaves in the tree. These branches tend to reach the class label of the leaves. Decision analysis needs a decision tree for decision-making. The decision tree illustrates the decisions that make it easy for decision-making \cite{XIA20-15}.

 \subsection{Deep Learning}

In machine learning and artificial intelligence (AI), a technique known as "deep learning" mimics human learning processes. As part of data science, deep learning is a critical feature. 
Data scientists benefit greatly from deep learning. must gather, analyze, and interpret massive, large amounts of data; it speeds up and simplifies the process. Predictive analytics may be made more efficient by using deep learning. While most machine learning algorithms are linear, deep learning algorithms are stacked in a hierarchical framework of increasing complexity and abstraction \cite{munppy89-16}.
